### 2013-12-06 paper.tex
init

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\ket}[1]{\ensuremath{\left|#1\right\rangle}}
\newcommand{\bra}[1]{\ensuremath{\left\langle#1\right|}}
\newcommand{\braket}[2]{\ensuremath{\left\langle #1 \middle| #2 \right\rangle}}
\newcommand{\obar}[1]{\ensuremath{\overline{ #1 }}}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
\graphicspath{ {C:/Users/Evan/Desktop/} }
\title{Relative Photometry of HD 227858 and HD 338931 from Landholt Standard SA 113475}
\author{Evan Ott \\ UT EID: eao466}
\date{\today}
\setcounter{secnumdepth}{0}
%\usepackage[parfill]{parskip}
\begin{document}
\maketitle
\section{Introduction}

\section{Methods}

\section{Results}

\section{Analysis}
$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
\begin{tabular}{c | c | c | c | c}
Star & Filter & X & $S_{*,sky}$ & $S_{sky}$ \\
\hline
HD 227858 & B & & 668721.3 & 1088003.27\\
HD 227858 & I & & 503371.8 & 427838.5534\\
HD 227858 & R & & 669765.3 & 1028251.386\\
HD 227858 & V & & 396151.3 & 700931.7268\\
HD 338931 & B & & 1118167 & 463203.7293\\
HD 338931 & I & & 1021443 & 422439.6612\\
HD 338931 & R & & 1062403 & 1035817.766\\
HD 338931 & V & & 567930 & 708921.9555\\
SA 113475 & B & & 139874.2 & 479501.2852\\
SA 113475 & I & & 461871.4 & 678267.3456\\
SA 113475 & R & & 643029.1 & 1699412.832\\
SA 113475 & V & & 367109.7 & 1110109.973\\
SA 113475 & B & & 565539.5 & 1492937.888\\
SA 113475 & I & & 1992206 & 4536981.855\\
SA 113475 & R & & 250266.8 & 626392.1272\\
SA 113475 & V & & 318196.8 & 983429.69\\
\end{tabular}

\section{Conclusion}

\begin{thebibliography}{9}

\end{thebibliography}

\end{document}

### 2013-12-06 paper.tex
updated vals for signal

@@
 
+\begin{tabular}{c | c | c | c | c}
+Star & Filter & $X=\sec{z}$ & $S_{*,sky}$ & $S_{sky}$ \\
+\hline
+HD 227858 & B & 1.147 & 549081 & 445607 \\
+HD 227858 & I & 1.156 & 437742 &  182394\\
+HD 227858 & R & 1.152 & 551039 & 438748\\
+HD 227858 & V & 1.150 & 320125 & 282855\\
+HD 338931 & B & 1.188 & 1078502 & 286905\\
+HD 338931 & I & 1.197 & 982646 & 254194\\
+HD 338931 & R & 1.194 & 996322 & 632289\\
+HD 338931 & V & 1.191 & 526991 & 443543\\
+SA 113475 & B & 1.150 & 139874 & 128880\\
+SA 113475 & I & 1.153 & 461871 & 186586\\
+SA 113475 & R & 1.151 & 643233 & 440040\\
+SA 113475 & V & 1.151 & 367110 & 294031\\
+SA 113475 & B & 1.428 & 565220 & 403841\\
+SA 113475 & I & 1.475 & 1991118 & 1138438\\
+SA 113475 & R & 1.454 & 251570 & 148624\\
+SA 113475 & V & 1.441 & 318197 & 264164
+\end{tabular}
+
 \section{Analysis}
 $S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
-\begin{tabular}{c | c | c | c | c}
-Star & Filter & X & $S_{*,sky}$ & $S_{sky}$ \\
-\hline
-HD 227858 & B & & 668721.3 & 1088003.27\\
-HD 227858 & I & & 503371.8 & 427838.5534\\
-HD 227858 & R & & 669765.3 & 1028251.386\\
-HD 227858 & V & & 396151.3 & 700931.7268\\
-HD 338931 & B & & 1118167 & 463203.7293\\
-HD 338931 & I & & 1021443 & 422439.6612\\
-HD 338931 & R & & 1062403 & 1035817.766\\
-HD 338931 & V & & 567930 & 708921.9555\\
-SA 113475 & B & & 139874.2 & 479501.2852\\
-SA 113475 & I & & 461871.4 & 678267.3456\\
-SA 113475 & R & & 643029.1 & 1699412.832\\
-SA 113475 & V & & 367109.7 & 1110109.973\\
-SA 113475 & B & & 565539.5 & 1492937.888\\
-SA 113475 & I & & 1992206 & 4536981.855\\
-SA 113475 & R & & 250266.8 & 626392.1272\\
-SA 113475 & V & & 318196.8 & 983429.69\\
-\end{tabular}
 

### 2013-12-06 paper.tex
stuff

--- 2013-12-06 paper.tex
@@
 
+\begin{tabular}{c | c | c | c | c | c}
+Star & Filter & $X=\sec{z}$ & $S_{*,sky}$ & $S_{sky}$ & $S_*$\\
+\hline
+HD 227858 & B & 1.147 & 549081 & 445607 & 103474\\
+HD 227858 & V & 1.150 & 320125 & 282855 & 37270\\
+HD 227858 & R & 1.152 & 551039 & 438748 & 112291\\
+HD 227858 & I & 1.156 & 437742 &  182394 & 255348\\
+HD 338931 & B & 1.188 & 1078502 & 286905 & 791597\\
+HD 338931 & V & 1.191 & 526991 & 443543 & 83448\\
+HD 338931 & R & 1.194 & 996322 & 632289 & 364033\\
+HD 338931 & I & 1.197 & 982646 & 254194 & 728452\\
+SA 113475 & B & 1.150 & 139874 & 128880 & 10994\\
+SA 113475 & V & 1.151 & 367110 & 294031 & 73079\\
+SA 113475 & R & 1.151 & 643233 & 440040 & 203193\\
+SA 113475 & I & 1.153 & 461871 & 186586 & 275285\\
+SA 113475 & B & 1.428 & 565220 & 403841 & 161379\\
+SA 113475 & V & 1.441 & 318197 & 264164 & 54033\\
+SA 113475 & R & 1.454 & 251570 & 148624 & 102946\\
+SA 113475 & I & 1.475 & 1991118 & 1138438 & 852680\\
+\end{tabular}
+
 \section{Analysis}
 $S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
-\begin{tabular}{c | c | c | c | c}
-Star & Filter & X & $S_{*,sky}$ & $S_{sky}$ \\
-\hline
-HD 227858 & B & & 668721.3 & 1088003.27\\
-HD 227858 & I & & 503371.8 & 427838.5534\\
-HD 227858 & R & & 669765.3 & 1028251.386\\
-HD 227858 & V & & 396151.3 & 700931.7268\\
-HD 338931 & B & & 1118167 & 463203.7293\\
-HD 338931 & I & & 1021443 & 422439.6612\\
-HD 338931 & R & & 1062403 & 1035817.766\\
-HD 338931 & V & & 567930 & 708921.9555\\
-SA 113475 & B & & 139874.2 & 479501.2852\\
-SA 113475 & I & & 461871.4 & 678267.3456\\
-SA 113475 & R & & 643029.1 & 1699412.832\\
-SA 113475 & V & & 367109.7 & 1110109.973\\
-SA 113475 & B & & 565539.5 & 1492937.888\\
-SA 113475 & I & & 1992206 & 4536981.855\\
-SA 113475 & R & & 250266.8 & 626392.1272\\
-SA 113475 & V & & 318196.8 & 983429.69\\
-\end{tabular}
 

### 2013-12-10 paper.tex
COEFFICIENT

--- 2013-12-06 paper.tex
@@
 
+\begin{center}
+\begin{tabular}{c | c | c | c | c | c }
+							%SUM              FLUX
+Star & Filter & t(s) & $X=\sec{z}$ & $S_{*,sky}=\mathsf{SUM}$ & $S_*=\mathsf{FLUX=SUM-MSKY*AREA}$\\
+\hline
+HD 227858 & B & 30 & 1.294 & 117809 & 39381 \\
+HD 227858 & V & 30 & 1.301 & 388133 & 131079  \\
+HD 227858 & R & 30 & 1.307 & 567655 & 254168  \\
+HD 227858 & I &  30 & 1.323 & 417430 & 260971   \\
+
+HD 338931 & B & 30 & 1.394 & 255793 & 152570 \\
+HD 338931 & V & 30 & 1.405 & 767017 & 494401  \\
+HD 338931 & R & 30 & 1.413 & 1390626 &  977589 \\
+HD 338931 & I & 30 &  1.424 & 1285304 &  1075136 \\
+
+SA 113475 & B & 30 & 1.206  & 169993 & 38822  \\
+SA 113475 & B & 30 & 1.482  & 179149 &  33471 \\
+
+SA 113475 & V & 30 & 1.207  & 477466 & 154874 \\
+SA 113475 & V & 30 & 1.498  & 665531 &  147737 \\
+
+SA 113475 & R & 30 & 1.209 & 802783  & 344417  \\
+SA 113475 & R & 30 & 1.498 & 1064716 & 332641 \\
+
+SA 113475 & I & 30 & 1.213 & 477466  & 154874  \\
+SA 113475 & I & 30 & 1.521& 665531 & 147737   \\
+
+\end{tabular}
+\end{center}
+
+From \ref{eq:ext} and reference data for SA 113475, we arrive at the extinction coefficients:
+\begin{align*}
+k_B&= 0.583\\
+k_V&= 0.176\\
+k_R&= 0.131\\
+k_I&= 0.166
+\end{align*}
+\begin{equation}
+\label{eq:ext}
+m_1-m_2=k(X_1-X_2)=-2.5\log_{10}\frac{S_1t_2}{S_2t_1}
+\end{equation}
 \section{Analysis}
 $S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
-\begin{tabular}{c | c | c | c | c}
-Star & Filter & X & $S_{*,sky}$ & $S_{sky}$ \\
-\hline
-HD 227858 & B & & 668721.3 & 1088003.27\\
-HD 227858 & I & & 503371.8 & 427838.5534\\
-HD 227858 & R & & 669765.3 & 1028251.386\\
-HD 227858 & V & & 396151.3 & 700931.7268\\
-HD 338931 & B & & 1118167 & 463203.7293\\
-HD 338931 & I & & 1021443 & 422439.6612\\
-HD 338931 & R & & 1062403 & 1035817.766\\
-HD 338931 & V & & 567930 & 708921.9555\\
-SA 113475 & B & & 139874.2 & 479501.2852\\
-SA 113475 & I & & 461871.4 & 678267.3456\\
-SA 113475 & R & & 643029.1 & 1699412.832\\
-SA 113475 & V & & 367109.7 & 1110109.973\\
-SA 113475 & B & & 565539.5 & 1492937.888\\
-SA 113475 & I & & 1992206 & 4536981.855\\
-SA 113475 & R & & 250266.8 & 626392.1272\\
-SA 113475 & V & & 318196.8 & 983429.69\\
-\end{tabular}
 

### 2013-12-10 paper.tex
getting somewhere

@@
 
-From \ref{eq:ext} and reference data for SA 113475, we arrive at the extinction coefficients:
+From Equation \ref{eq:ext} and reference data for SA 113475, we arrive at the extinction coefficients:
 \begin{align*}
@@
 \label{eq:ext}
-m_1-m_2=k(X_1-X_2)=-2.5\log_{10}\frac{S_1t_2}{S_2t_1}
+m_a-m_a'=k(X_a-X_a')=-2.5\log_{10}\frac{S_at_a'}{S_a't_a}
 \end{equation}
+
+With known magnitudes of a calibration star, we can use Equation \ref{eq:targetstar} to determine the magnitude of
+the target star, $m_*$.
+\begin{equation}
+\label{eq:targetstar}
+m_{rel,*}=m_*-m_r=k(X_r-X_*)-2.5\log_{10}\frac{S_*t_r}{S_rt_*}
+\end{equation}
+So relative to SA 113475, the target stars have relative magnitudes: FIXME add in intrinsic - it's ok
+\begin{center}
+\begin{tabular}{c | c | c }
+Star & Filter & $m_{rel,*}$\\
+\hline
+HD 227858 & B & -0.067 \\
+HD 227858 & V & +0.165 \\
+HD 227858 & R & +0.317  \\
+HD 227858 & I &   -0.585 \\
+
+HD 338931 & B & -1.596 \\
+HD 338931 & V & -1.295 \\
+HD 338931 & R &  -1.160\\
+HD 338931 & I & -2.190 \\
+\end{tabular}
+\end{center}
+
+k tells us what the observed magnitude (m_obs = kX + m_int)
+
 \section{Analysis}
 $S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
+
+FIXME
+We can determine the precise relationship between flux and signal for each filter as well, using Equation \ref{eq:convert}
+\begin{equation}
+S_{*,sky}=\frac{\Delta\nu \obar{\Phi}t\obar{f}A}{g}
+\label{eq:convert}
+\end{equation}
+where $\obar{f}$ is the averaged flux in the filter band, $t$ is the exposure time, $A$ is the aperture of the telescope (area at entry),
+$g$ is the gain in electrons per count, $\obar{\Phi}=\obar{ql\phi}$ is the averaged response of the system over the filter, and $\Delta\nu$ is the
+bandwidth of the filter.
 

### 2013-12-10 paper.tex
getting there

--- 2013-12-06 paper.tex
@@
 \graphicspath{ {C:/Users/Evan/Desktop/} }
-\title{Relative Photometry of HD 227858 and HD 338931 from Landholt Standard SA 113475}
+\title{Determination of Magnitude and Intrinsic Flux of HD 227858 and HD 338931 from Landholt Standard SA 113475}
 \author{Evan Ott \\ UT EID: eao466}
@@
 \section{Introduction}
+While the casual astrophotographer might only care about seeing as many stars as possible in an image, in academic astronomy,
+we often want to have quantifiable data about stars, for example the magnitude (measure of brightness) of the star to compare it
+to others, either in terms of total light or broken into sections of the electromagnetic spectrum by filters. Or, we might want to
+have the flux (photon energy or number per area each second). However, besides having proper equipment, much calibration
+must take place to account for all present factors - atmospheric extinction of photons travelling at different angles
+through Earth's atmosphere, ever-present and never-present pixels in our sensor, absorption in mirrors and lenses, etc.
+Here, I work through calculating the magnitude and intrinsic flux (flux just outside the atmosphere) of stars HD 227858
+and HD 338931 based on the Landhold Standard star SA 113475{\huge\cite{lanholt}}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c | c}
+Filter & $\lambda_0$ & $\Delta\nu$ & Absolute Spectral Radiance  \\
+ & [$\mu$m]& [Hz]& [erg cm$^{-2}$s$^{-1}$\AA$^{-1}$] \\
+\hline
+B & 0.44 & 3.06E15 & 6.60E-9 \\
+V & 0.55& 3.37E15 &3.64E-9 \\
+R & 0.70& 1.36E15 &1.36E-9 \\
+I & 0.90& 6.81E14&8.30E-10
+\end{tabular}
+\end{center}
+\caption{Johnson Filter Band parameters, with $\lambda_0$ as the central wavelenth,
+$\Delta\nu$ as the FWHM of frequency of the filter and absolute spectral radiance as the
+flux per wavelength to be observed through the filter for a 0-magnitude star in the band.}
+\label{table:filters}
+\end{table}
 
 \section{Methods}
+Using the 16" telescope in Robert Lee Moore Hall at the University of Texas at Austin, I and my classmates used a 1024x1024 CCD imaging
+system, coupled with a selection of Johnson-type filters for the B, V, R, and I parts of the spectrum. Parameters of the filters can be found in Table
+\ref{table:filters}. After taking dark frame and flat frame images (to account for the CCD's inherent background response to temperature and
+non-uniform sensitivity, respectively), we were able to use the IRAF suite of programs to isolate the count (in Arbitrary Data Units [ADU])
+in the image due to photons from the stars of interest and the count associated with background light from other sources. These data
+are found in Table \ref{table:Counts}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c | c | c | c }
+Star & Filter & t & $X=\sec{z}$ & $S_{*,sky}$ & $S_*$\\
+ &  & [s]&  & $\mathsf{SUM}$ & $\mathsf{FLUX=SUM-MSKY*AREA}$\\
+\hline
+HD 227858 & B & 30 & 1.294 & 117809 & 39381 \\
+HD 227858 & V & 30 & 1.301 & 388133 & 131079  \\
+HD 227858 & R & 30 & 1.307 & 567655 & 254168  \\
+HD 227858 & I &  30 & 1.323 & 417430 & 260971   \\
+HD 338931 & B & 30 & 1.394 & 255793 & 152570 \\
+HD 338931 & V & 30 & 1.405 & 767017 & 494401  \\
+HD 338931 & R & 30 & 1.413 & 1390626 &  977589 \\
+HD 338931 & I & 30 &  1.424 & 1285304 &  1075136 \\
+SA 113475 & B & 30 & 1.206  & 169993 & 38822  \\
+SA 113475 & B & 30 & 1.482  & 179149 &  33471 \\
+SA 113475 & V & 30 & 1.207  & 477466 & 154874 \\
+SA 113475 & V & 30 & 1.498  & 665531 &  147737 \\
+SA 113475 & R & 30 & 1.209 & 802783  & 344417  \\
+SA 113475 & R & 30 & 1.498 & 1064716 & 332641 \\
+SA 113475 & I & 30 & 1.213 & 477466  & 154874  \\
+SA 113475 & I & 30 & 1.521& 665531 & 147737   \\
+\end{tabular}
+\caption{Signal for each target star as extracted from IRAF's ${\texttt{apphot phot}}$ function, presented with
+signal including background signal ($S_{*,sky}$), and signal with sky removed ($S_*$). $t$ is the exposure time in seconds,
+and $X$ is the airmass given as the secant of the zenith angle of the observation.}
+\label{table:Counts} 
+\end{center}
+\end{table}
+
+To determine the relative magnitudes of the target stars, it is sufficient to account for two factors: atmospheric extinction
+and airmass. Airmass is simply a measure of how much of the atmosphere relative to the most direct path ($z=0$) the photon
+had to travel and atmospheric extinction is a loss of photons due to absorption in the atmosphere before reaching the telescope.
+For a single star $a$ measured once with airmass $X$, and exposure time $t$, giving rise to signal $S$, then measured again
+with $X',~t'$ giving $S'$, we have the relation given in Equation \ref{eq:ext},
+
+\begin{equation}
+\label{eq:ext}
+m_a-m_a'=k(X_a-X_a')=-2.5\log_{10}\frac{S_at_a'}{S_a't_a}
+\end{equation}
+
+where $m_a$ and $m_a'$ are the associated apparent magnitudes of the star in the different positions in the sky and $k$ is the
+extinction coefficient (in the filter band used). From the $S-X$ data in Table \ref{table:Counts} for our standard star, we can
+calculate the extinction coefficients for each filter band (see Table \ref{table:coeff}).
+
+From Equation \ref{eq:ext} and reference data for SA 113475, we arrive at the extinction coefficients in Table \ref{table:coeff}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c}
+Filter & k \\
+\hline
+B& 0.583\\
+V&0.176\\
+R& 0.131\\
+I&0.166
+\end{tabular}
+\end{center}
+\caption{Extinction coefficients determined from the two observations of SA 113475 as seen in Table \ref{table:Counts} using Equation \ref{eq:ext}.}
+\label{table:coeff}
+\end{table}
+
+If we generalize Equation \ref{eq:ext} to account for comparing two different stars (which would not in general have the same absolute brightness),
+we arrive at Equation \ref{eq:targetstar}. Equation \ref{eq:targetstar} allows for the simple calculation of $m_*$, the magnitude
+of the target star, given information already known with the sole addition of the magnitude of the reference star, which is found in Table
+\ref{table:SAmag}.
+
+\begin{equation}
+\label{eq:targetstar}
+m_*-m_r=k(X_r-X_*)-2.5\log_{10}\frac{S_*t_r}{S_rt_*}
+\end{equation}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c}
+Filter & Intrinsic Magnitude \\
+\hline
+B & 11.362 \\
+V &  10.304\\
+R & 9.736\\
+I & 9.208
+\end{tabular}
+\end{center}
+\caption{Intrinsic magnitude of SA 113475 from \huge FIXME FIXME FIXME}
+\label{table:SAmag}
+\end{table}
+
+Applying Equation \ref{eq:targetstar} gives us the intrinsic magnitude of each of our target stars as seen in Table \ref{table:relmag}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c }
+Star & Filter & $m_*$\\
+\hline
+HD 227858 & B & +11.295\\
+HD 227858 & V & +10.469 \\
+HD 227858 & R & +10.053 \\
+HD 227858 & I &   +8.623 \\
+HD 338931 & B & +9.766 \\
+HD 338931 & V & +9.009\\
+HD 338931 & R &  +8.576\\
+HD 338931 & I & +7.018
+\end{tabular}
+\end{center}
+\caption{Based on Table \ref{table:SAmag} and Equation \ref{eq:targetstar}, the intrinsic magnitudes of the target stars.}
+\label{table:relmag}
+\end{table}
+
+To calculate flux of the target stars, we need the flux from a reference star. While our reference star was able to provide enough information to relate magnitudes,
+these magnitudes, even coupled with signals are insufficient to provide more than a ratio. However, the ``absolute spectral irradiance''
+aspect of the filter is defined to be the physical flux that would pass through the filter for a 0-magnitude source. Thus, rewriting Equation
+\ref{eq:targetstar} to solve for flux, given $f_0$ for the filter, we can calculate the flux of our reference star with Equation \ref{eq:zeroflux}. 
+The measured flux for SA 113475 is given in Table \ref{table:SAflux}.
+
+\begin{equation}
+\label{eq:zeroflux}
+f_{ref}=f_010^{-(m_{ref}+k(X_{ref}-1))/2.5}
+\end{equation}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c}
+Filter & Measured Flux \\
+& [erg cm$^{-2}$s$^{-1}$]\\
+\hline
+B & 7.44E-10\\
+V & 1.46E-9\\
+R & 1.18E-9\\
+I & 1.5E-9
+\end{tabular}
+\caption{Flux for SA 113475 by filter for $X\approx1.21$, calculated with Equation \ref{eq:zeroflux} from Table \ref{table:filters}
+and Table \ref{table:SAmag}, and extinction coefficients in Table \ref{table:coeff}.}
+\label{table:SAflux}
+\end{center}
+\end{table}
+
+We can now do some algebraic sleuthing to determine how our telescope reacts to light with each filter. For a given filter,
+we have that $S_*=\frac{\Delta\nu{\obar{\Phi}}t{\obar{f_*}}A}{g}$ where $\Delta\nu$ is the FWHM of the filter in frequency,
+$t$ is the exposure time, $A$ is the aperture of the telescope, $g$ is the system gain, $f_*$ is the measured flux
+of the star, $S_*$ is the measured signal from the star and $\obar\Phi$ is the averaged impact of losses due to reflection, transmission, etc.
+By converting the flux from an energy flux to photon flux then that photon flux to number of photons per area per time (see Equation
+\ref{eq:signalflux}), we can calculate $R$, the system response, which is the average number of counts generated per photon in the filter band. 
+With the signal data from Table \ref{table:Counts} for SA 113475, 
+coupled with Equation \ref{eq:signalflux}, we arrive at the signal responses in \ref{table:response}.
+
+\begin{equation}
+\label{eq:signalflux}
+S_*=\frac{\Delta\nu{\obar{\Phi}}\frac{hc}{\lambda_0}}{g}n_\gamma=R\cdot n_\gamma
+\end{equation}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c}
+Filter & Signal Response \\
+& [count photon$^{-1}$]\\
+\hline
+B & 0.0061\\
+V & 0.0100\\
+R & 0.0216\\
+I & 0.0076
+\end{tabular}
+\caption{Signal response for each Johnson-type filter in ADU count per photon.}
+\label{table:response}
+\end{center}
+\end{table}
+
+A handy consequence of Equation \ref{eq:signalflux} is that using the same filter and telescope setup for two
+stars at the same exposure time gives $\frac{S_1}{S_2}=\frac{f_1}{f_2}$. As such, we can easly calculate the measured flux
+of each target star for each filter (see Table \ref{table:fluxes}).
+
+% $A=1280cm^2$ for the telescope, $t=30s$ for our dataset, and 
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c}
+Star& Filter & Measured Flux\\
+& &[erg cm$^{-2}$s$^{-1}$]\\
+\hline
+HD 227858 & B & 7.55E-10\\
+HD 227858 & V & 1.24E-9\\
+HD 227858 & R & 8.71E-10\\
+HD 227858 & I & 2.53E-9\\
+HD 338931 &B & 2.92E-9\\
+HD 338931 &V & 4.66E-9\\
+HD 338931 &R & 3.35E-9\\
+HD 338931 & I & 1.04E-8\\
+\end{tabular}
+\caption{FIXME}
+\label{table:fluxes}
+\end{center}
+\end{table}
 
 \section{Results}
+Assuming $g=3.0e^-/ADU$, and that each incoming photon that is not scattered, absorbed, or reflected energizes one electron,
+the flux at the top of the telescope should be 3.0 times that as measured. If we apply Equation \ref{eq:realflux}, which expresses the
+non-atmospherically-extincted flux as a function of airmass and measured flux (in this case, just above the telescope), we arrive at the
+intrinsic flux for each star as stated in Table \ref{table:realflux}.
 
-\begin{tabular}{c | c | c | c | c | c}
-Star & Filter & $X=\sec{z}$ & $S_{*,sky}$ & $S_{sky}$ & $S_*$\\
+\begin{equation}
+\label{eq:realflux}
+F=f10^{\frac{kX}{2.5}}
+\end{equation}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c | c | c | c}
+Star & Filter & Intrinsic Magnitude & Intrinsic Flux \\
+& & & [erg cm$^{-2}$s$^{-1}$] \\
 \hline
-HD 227858 & B & 1.147 & 549081 & 445607 & 103474\\
-HD 227858 & V & 1.150 & 320125 & 282855 & 37270\\
-HD 227858 & R & 1.152 & 551039 & 438748 & 112291\\
-HD 227858 & I & 1.156 & 437742 &  182394 & 255348\\
-HD 338931 & B & 1.188 & 1078502 & 286905 & 791597\\
-HD 338931 & V & 1.191 & 526991 & 443543 & 83448\\
-HD 338931 & R & 1.194 & 996322 & 632289 & 364033\\
-HD 338931 & I & 1.197 & 982646 & 254194 & 728452\\
-SA 113475 & B & 1.150 & 139874 & 128880 & 10994\\
-SA 113475 & V & 1.151 & 367110 & 294031 & 73079\\
-SA 113475 & R & 1.151 & 643233 & 440040 & 203193\\
-SA 113475 & I & 1.153 & 461871 & 186586 & 275285\\
-SA 113475 & B & 1.428 & 565220 & 403841 & 161379\\
-SA 113475 & V & 1.441 & 318197 & 264164 & 54033\\
-SA 113475 & R & 1.454 & 251570 & 148624 & 102946\\
-SA 113475 & I & 1.475 & 1991118 & 1138438 & 852680\\
+HD 227858 & B & 11.295 & 1.29E-8\\
+HD 227858 & V & 10.469  & 6.30E-9\\
+HD 227858 & R & 10.053 & 3.88E-9\\
+HD 227858 & I  & 8.623 & 1.26E-8\\
+HD 338931 & B & 9.766 & 5.69E-8\\
+HD 338931 & V & 9.009  & 2.47E-8\\
+HD 338931 & R & 8.576 & 1.54E-8\\
+HD 338931 & I & 7.018 & 5.38E-8\\
+SA 113475 & B & 11.362 & 1.13E-8\\
+SA 113475 & V & 10.304 & 7.14E-9\\
+SA 113475 & R  & 9.736 & 5.10E-9\\
+SA 113475 & I  & 9.208 & 7.15E-9\\
 \end{tabular}
+\caption{FIXME}
+\label{table:realflux}
+\end{center}
+\end{table}
 
 \section{Analysis}
-$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
 

### 2013-12-10 paper.tex
done

@@
 \graphicspath{ {C:/Users/Evan/Desktop/} }
-\title{Determination of Magnitude and Intrinsic Flux of HD 227858 and HD 338931 from Landholt Standard SA 113475}
+\title{Determination of Magnitude and Intrinsic Flux of HD 227858 and HD 338931 from Landolt Standard SA 113475}
 \author{Evan Ott \\ UT EID: eao466}
@@
 must take place to account for all present factors - atmospheric extinction of photons travelling at different angles
-through Earth's atmosphere, ever-present and never-present pixels in our sensor, absorption in mirrors and lenses, etc.
-Here, I work through calculating the magnitude and intrinsic flux (flux just outside the atmosphere) of stars HD 227858
-and HD 338931 based on the Landhold Standard star SA 113475{\huge\cite{lanholt}}.
+through Earth's atmosphere, ever-present and never-present pixels in sensors, absorption in mirrors and lenses, etc.
+Here, I work through calculating the magnitude and intrinsic flux (flux just outside the atmosphere) of stars HD 227858 (see Figure \ref{fig:hd2})
+and HD 338931 (see Figure \ref{fig:hd3}) based on the Landolt Standard star SA 113475 (see Figure \ref{fig:sa})\cite{landolt}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.75]{hd2.jpg}
+\caption{\label{fig:hd2} HD 227585 and surrounding stars, colored by linear scale in number of counts per pixel.}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.75]{hd3.jpg}
+\caption{\label{fig:hd3} HD 338931 and surrounding stars, colored by linear scale in number of counts per pixel.}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.75]{sa1.jpg}
+\caption{\label{fig:sa} Landolt Standard star SA 113475 and surrounding stars, colored by linear scale in number of counts per pixel.}
+\end{figure}
 
@@
 \section{Methods}
-Using the 16" telescope in Robert Lee Moore Hall at the University of Texas at Austin, I and my classmates used a 1024x1024 CCD imaging
-system, coupled with a selection of Johnson-type filters for the B, V, R, and I parts of the spectrum. Parameters of the filters can be found in Table
+Using the 16" telescope at Robert Lee Moore Hall at the University of Texas at Austin, I and my classmates used a 1024x1024 CCD imaging
+system, coupled with a selection of Johnson-type filters for the B, V, R, and I parts of the spectrum to analyse HD 227858 and HD 338931. Parameters of the filters can be found in Table
 \ref{table:filters}. After taking dark frame and flat frame images (to account for the CCD's inherent background response to temperature and
@@
 \hline
-B & 11.362 \\
-V &  10.304\\
-R & 9.736\\
-I & 9.208
+B & 11.362 $\pm$ 0.0006\\
+V &  10.304 $\pm$ 0.0004\\
+R & 9.736 $\pm$ 0.0006\\
+I & 9.208 $\pm$ 0.0008
 \end{tabular}
 \end{center}
-\caption{Intrinsic magnitude of SA 113475 from \huge FIXME FIXME FIXME}
+\caption{Intrinsic magnitude of SA 113475 from Landolt \cite{landolt}.}
 \label{table:SAmag}
@@
 \label{eq:signalflux}
-S_*=\frac{\Delta\nu{\obar{\Phi}}\frac{hc}{\lambda_0}}{g}n_\gamma=R\cdot n_\gamma
+S_*=\frac{\Delta\nu{\obar{\Phi}}t{\obar{f_*}}A}{g}=\frac{\Delta\nu{\obar{\Phi}}\frac{hc}{\lambda_0}}{g}n_\gamma=R\cdot n_\gamma
 \end{equation}
@@
 A handy consequence of Equation \ref{eq:signalflux} is that using the same filter and telescope setup for two
-stars at the same exposure time gives $\frac{S_1}{S_2}=\frac{f_1}{f_2}$. As such, we can easly calculate the measured flux
+stars with the same exposure time gives $\frac{S_1}{S_2}=\frac{f_1}{f_2}$. As such, we can easly calculate the measured flux
 of each target star for each filter (see Table \ref{table:fluxes}).
 
-% $A=1280cm^2$ for the telescope, $t=30s$ for our dataset, and 
 \begin{table}
@@
 \end{tabular}
-\caption{FIXME}
+\caption{Measured flux of target stars based on the measured flux of SA 113475.}
 \label{table:fluxes}
@@
 \label{eq:realflux}
-F=f10^{\frac{kX}{2.5}}
+F=f\cdot10^{kX/2.5}
 \end{equation}
@@
 HD 338931 & I & 7.018 & 5.38E-8\\
-SA 113475 & B & 11.362 & 1.13E-8\\
-SA 113475 & V & 10.304 & 7.14E-9\\
-SA 113475 & R  & 9.736 & 5.10E-9\\
-SA 113475 & I  & 9.208 & 7.15E-9\\
+SA 113475 & B & 11.362* & 1.13E-8\\
+SA 113475 & V & 10.304* & 7.14E-9\\
+SA 113475 & R  & 9.736* & 5.10E-9\\
+SA 113475 & I  & 9.208* & 7.15E-9\\
 \end{tabular}
-\caption{FIXME}
+\caption{Final results (minus uncertainties) for the magnitude and flux of each target star in each filter band. *Values are from \cite{landolt}.}
 \label{table:realflux}
@@
 \section{Analysis}
+From Equation \ref{eq:targetstar}, we can calculate the uncertainty in target star magnitudes, target star fluxes, and atmospheric extinction coefficients.
+For general function $f=f(x_1, x_2, ..., x_n)$, we expect: $$\sigma_f^2=\Sigma_{i=1}^{n}(\partial_{x_i}f(x_1, x_2, ..., x_n)\sigma_{x_i})^2$$
+Thus for magnitudes of target stars, we have:
+\begin{equation*}
+\sigma_{m_1}^2=\sigma_{m_2}^2+6.25\left(\left(\frac{\sigma_{t_1}}{t_1}\right)^2+\left(\frac{\sigma_{S_1}}{S_1}\right)^2
++\left(\frac{\sigma_{t_2}}{t_2}\right)^2+\left(\frac{\sigma_{S_2}}{S_2}\right)^2\right) + 4k^2\sigma_X^2+\sigma_k^2(X_1-X_2)^2
+\end{equation*}
+For extinction coefficients, we have:
+\begin{equation*}
+\sigma_k^2/6.25=\left(\frac{\sigma_{t_1}}{t_1}\right)^2+\left(\frac{\sigma_{S_1}}{S_1}\right)^2
++\left(\frac{\sigma_{t_2}}{t_2}\right)^2+\left(\frac{\sigma_{S_2}}{S_2}\right)^2
++\log_{10}\left(\frac{S_1t_2}{S_2t_1}\right)(X_1-X_2)^{-2}(\sigma_{X_1}^2+\sigma_{X_2}^2)
+\end{equation*}
+For flux, we arrive at:
+\begin{equation*}
+\sigma_{f_1}^2=f_1^2\left[
+\frac{\sigma_{f_2}^2}{f_2^2}+\frac{\ln10}{6.25}\left(
+\sigma_{m_1}^2+\sigma_{m_2}^2+\sigma_k^2(X_1-X_2)^2+k^2(\sigma_{X_1}^2+\sigma_{X_2}^2)
+\right)
+\right]
+\end{equation*}
+And finally, for system response, we know $nR=S$ and $n=\frac{fAt\lambda_0}{hc}$, so we arrive at
+\begin{align*}
+\sigma_R^2=&\frac{\sigma_S^2}{n^2}+\frac{S^2\sigma_n^2}{n^4} \\
+\sigma_n^2=&n^2\left(\frac{\sigma_f^2}{f^2}+\frac{\sigma_A^2}{A^2}+\frac{\sigma_t^2}{t^2}\right)\\
+\sigma_S^2=&S
+\end{align*}
+For our known uncertainties, we have the uncertainty in magnitude of SA 113475 from the literature, $t=30s$,
+$\sigma_t\approx0.001s$,
+$A=1280cm^2$,
+$\sigma_A\approx.5\textrm{cm}^2$,
+$\sigma_X\approx0.01$, and $\sigma_S^2=S$. This and data above are sufficient to calculate the error in $k$ for each filter,
+which can then be used to calculate the error in magnitudes and flux (each by starting with known error in measurement of stars).
 
 \section{Conclusion}
+With magnitude of HD 227858 having an accepted value of $B=11.20\pm0.05,~V=10.76\pm0.06$ \cite{hd2}, with the observed value from the RLM
+telescope for $B$ within two standard deviations but $V$ is not within 4.5$\sigma_V$, surely there must be unaccounted for sources of error,
+potentially including human error in processing the raw data or collecting the original images. To be fair, without full calculation
+of error in my measurement which I have detailed but not completed, it is entirely possible that the standard error on my measurement
+is sufficiently large as to account for this difference due simply to uncertainty. However, with accepted values $B=9.72,~V=9.14$\cite{hd3}
+for HD 338931, the observed values are within 1\% and 1.5\% respectively (no error given in \cite{hd3}), it would appear likely that
+the observed values here are indeed consistent.
+
+This shows that although the RLM telescope is in the heart of air- and light-polluted Austin, Texas and is miniscule compared to UT's own
+telescopes at the McDonald Observatory, real, workable data is attainable with the right mathematical framework. Furthermore, continuing
+to take measurements of additional stars would help in calibrating results (rather than basing the extinction coefficient for a filter
+on two reduced samples).
 
 \begin{thebibliography}{9}
+\bibitem{hd2} H\o{t}, E., et al. ``The Tycho-2 catalogue of the 2.5 million brightest stars''. {\emph{Astronomy and Astrophysics}} v.355, p.L27-L30. (2000)
+\bibitem{landolt} Landolt, A.U. ``{\emph{UBVRI}} Photometric Standard Stars Around the Celestial Equator: Updates and Additions''. {\emph{The
+Astronomical Journal}}. {\bf{137}} 4186. (2009) \url{http://iopscience.iop.org/1538-3881/137/5/4186}
+\bibitem{hd3} Reed, B.C. ``Catalog of Galactic OB Stars''. {\emph{The Astronomical Journal}}. {\bf{125}} 2531. (2003)
+\url{http://iopscience.iop.org/1538-3881/125/5/2531/}
 
